Untitled

### 2025-02-24 script/internet_weighted.Rmd
import folders

#3G Data
##2019
###ADM2
*Note pays:
BEN: 2018
BFA: 2014
BWA: /
CMR: 2017
CIV: /
GHA: 2014
GIN: 2012
KEN: 2013
LBR: 2013
MLI: /
MWI: 2014
MOZ: /
NAM: /
NER: 2013
NGA: 2012
SEN: 2015
SLE: 2014
TZA: 2014
UGA: 2013
ZMB: 2014
ZWE: 2015
```{r}
countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE", "CMR", "NAM", "GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")

#No Botswana, Ivory Coast, Mali ,Togo in 2018

@@

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_ggg_pop_2=pot_ggg_pop,
         mean_ggg_pop_2=mean_ggg_pop,
         mean_pop_2=mean_pop,
         mean_ggg_2=mean_ggg)

data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)
```

@@

```{r}
countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE", "GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")

#No Botswana, Ivory Coast, Mali ,Togo in 2018

@@

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_ggg_pop_2=pot_ggg_pop,
         mean_ggg_pop_2=mean_ggg_pop,
         mean_pop_2=mean_pop,
         mean_ggg_2=mean_ggg)

@@

data_trust %<>%
  mutate(mean_ggg_2 = coalesce(mean_ggg_2.x, mean_ggg_2.y))%>%
  mutate(mean_ggg_pop_2 = coalesce(mean_ggg_pop_2.x, mean_ggg_pop_2.y))%>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  mutate(pot_ggg_pop_2 = coalesce(pot_ggg_pop_2.x, pot_ggg_pop_2.y))%>%
  select(-c(mean_ggg_2.x, mean_ggg_2.y, mean_ggg_pop_2.x,mean_ggg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_ggg_pop_2.x, pot_ggg_pop_2.y))

@@

@@

##2014
###ADM2
```{r}
countries_adm2 <- c("GIN", "LBR", "NER", "KEN","NGA","UGA", "ZWE")

#No Benin, Botswana, Cameroon, Ivory Coast, Mali, Namibia, Senegal, Togo in 2014

@@

data_trust %<>%
  mutate(mean_ggg_2 = coalesce(mean_ggg_2.x, mean_ggg_2.y))%>%
  mutate(mean_ggg_pop_2 = coalesce(mean_ggg_pop_2.x, mean_ggg_pop_2.y))%>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  mutate(pot_ggg_pop_2 = coalesce(pot_ggg_pop_2.x, pot_ggg_pop_2.y))%>%
  select(-c(mean_ggg_2.x, mean_ggg_2.y, mean_ggg_pop_2.x,mean_ggg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_ggg_pop_2.x, pot_ggg_pop_2.y))

@@

#2G Data

@@

```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

#No Senegal, Togo in 2019

@@

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_gg_pop_2=pot_gg_pop,
         mean_gg_pop_2=mean_gg_pop,
         mean_pop_2=mean_pop,
         mean_gg_2=mean_gg)

data_trust %<>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  select(-c(mean_pop_2.x, mean_pop_2.y))

@@

```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE", "GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")
#No Senegal, Togo in 2016

@@

glimpse(accumulated_results)

accumulated_results%<>%
  rename(pot_gg_pop_2=pot_gg_pop,
         mean_gg_pop_2=mean_gg_pop,
         mean_pop_2=mean_pop,
         mean_gg_2=mean_gg)

@@

data_trust %<>%
  mutate(mean_gg_2 = coalesce(mean_gg_2.x, mean_gg_2.y))%>%
  mutate(mean_gg_pop_2 = coalesce(mean_gg_pop_2.x, mean_gg_pop_2.y))%>%
  mutate(mean_pop_2 = coalesce(mean_pop_2.x, mean_pop_2.y))%>%
  mutate(pot_gg_pop_2 = coalesce(pot_gg_pop_2.x, pot_gg_pop_2.y))%>%
  select(-c(mean_gg_2.x, mean_gg_2.y, mean_gg_pop_2.x,mean_gg_pop_2.y, mean_pop_2.x, mean_pop_2.y, pot_gg_pop_2.x, pot_gg_pop_2.y))

@@

@@

>>>>

#3G Maps
##2016
###ADM2

*Note pays:
BEN: /
BFA: 2014
BWA: /
CMR: /
CIV: /
GHA: 2014
GIN: 2012
KEN: 2013
LBR: 2013
MLI: /
MWI: 2014
MOZ: /
NAM: /
NER: 2013
NGA: 2012
SEN: 2015
SLE: 2014
TZA: 2014
UGA: 2013
ZMB: 2014
ZWE: 2015

```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE")
#No Botswana, Ivory Coast, Mali ,Togo in 2018

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/3G/"

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==7)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "3G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 3G Coverage ADM2 - Round 7", sep = " "))

  ggsave(filename = paste0(output_dir, country, "3G_weighted_map_r7.jpg"), plot = plot, width = 10, height = 8)

```
###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")

countries_adm1 <- c("GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/3G/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

panel_sf <- data_trust_report_adm1_valid %>%
  filter(ISO == country, round==7)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "3G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 3G Coverage ADM1 - Round 7", sep = " "))

  ggsave(filename = paste0(output_dir, country, "3G_weighted_map_r7.jpg"), plot = plot, width = 10, height = 8)

##2014
###ADM2
```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("GIN", "LBR", "NER")
#No Benin, Botswana, Cameroon, Ivory Coast, Mali, Namibia, Senegal, Togo in 2015

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/3G/"

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "3G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 3G Coverage ADM2 - Round 6", sep = " "))

  ggsave(filename = paste0(output_dir, country, "3G_weighted_map_r6.jpg"), plot = plot, width = 10, height = 8)

```
###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")

countries_adm1 <- c("KEN","NGA","UGA", "ZWE")
# No Mozambique in 2015

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/3G/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

panel_sf <- data_trust_report_adm1_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "3G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 3G Coverage ADM1 - Round 6", sep = " "))

  ggsave(filename = paste0(output_dir, country, "3G_weighted_map_r6.jpg"), plot = plot, width = 10, height = 8)

#2G Maps
*Note pays 2G
BEN: 2008
BFA: 2014
BWA: 2011
CMR: 2015
CIV: 2006
GHA: 2014
GIN: 2012
KEN: 2011
LBR: 2013
MLI: 2004
MWI: 2008
MOZ: 2013
NAM: 2008
NER: 2014
NGA: 2012
SEN: /
SLE: 2014
TZA: 2008
UGA: 2009
ZMB: 2008
ZWE: 2012

##2016
###ADM2
```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
#No Senegal, Togo in 2018

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==7)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 2G Coverage ADM2 - Round 7", sep = " "))

  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r7.jpg"), plot = plot, width = 10, height = 8)

###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")

countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==7)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 2G Coverage ADM1 - Round 7", sep = " "))

  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r7.jpg"), plot = plot, width = 10, height = 8)

}
```
##2014
*Note pays 2G
BEN: 2008
BFA: 2014
BWA: 2011
CMR: 2015
CIV: 2006
GHA: 2014
GIN: 2012
KEN: 2011
LBR: 2013
MLI: 2004
MWI: 2008
MOZ: 2013
NAM: 2008
NER: 2014
NGA: 2012
SEN: /
SLE: 2014
TZA: 2008
UGA: 2009
ZMB: 2008
ZWE: 2012

###ADM2
```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
#No Senegal, Togo in 2015

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 2G Coverage ADM2 - Round 6", sep = " "))

  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r6.jpg"), plot = plot, width = 10, height = 8)

```
###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")

countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 2G Coverage ADM1 - Round 6", sep = " "))

  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r6.jpg"), plot = plot, width = 10, height = 8)

}
```
##2011
*Note pays 2G
BEN: 2008
BFA: 2014
BWA: 2011
CMR: 2015
CIV: 2006
GHA: 2014
GIN: 2012
KEN: 2011
LBR: 2013
MLI: 2004
MWI: 2008
MOZ: 2013
NAM: 2008
NER: 2014
NGA: 2012
SEN: /
SLE: 2014
TZA: 2008
UGA: 2009
ZMB: 2008
ZWE: 2012

###ADM2
```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
#No Senegal, Togo in 2013

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 2G Coverage ADM2 - Round 5", sep = " "))

  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r5.jpg"), plot = plot, width = 10, height = 8)

```
###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")

countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/2G/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = pot_gg_pop), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "2G Coverage", breaks = c(min(regions$pot_gg_pop), max(regions$pot_gg_pop)), labels = c(0, 1)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- 2G Coverage ADM1 - Round 5", sep = " "))

  ggsave(filename = paste0(output_dir, country, "2G_weighted_map_r5.jpg"), plot = plot, width = 10, height = 8)

}
```

#3G Data
##2019
###ADM2
*Note pays:
BEN: 2018
BFA: 2014
BWA: /
CMR: 2017
CIV: /
GHA: 2014
GIN: 2012
KEN: 2013
LBR: 2013
MLI: /
MWI: 2014
MOZ: /
NAM: /
NER: 2013
NGA: 2012
SEN: 2015
SLE: 2014
TZA: 2014
UGA: 2013
ZMB: 2014
ZWE: 2015
```{r}
countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE", "CMR", "NAM")
#No Botswana, Ivory Coast, Mali ,Togo in 2018

glimpse(afro_w8)

@@

afro_w8 %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

glimpse(afro_w8)

afro_w8%<>%
  distinct(id_unique, .keep_all = TRUE)

###ADM1
```{r}
countries_adm1 <- c("GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
  mutate(round=8)

afro_w8 %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

afro_w8 %<>%
  mutate(mean_ggg = coalesce(mean_ggg.x, mean_ggg.y))%>%
  mutate(mean_ggg_pop = coalesce(mean_ggg_pop.x, mean_ggg_pop.y))%>%
  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
  mutate(pot_ggg_pop = coalesce(pot_ggg_pop.x, pot_ggg_pop.y))%>%
  select(-c(mean_ggg.x, mean_ggg.y, mean_ggg_pop.x,mean_ggg_pop.y, mean_pop.x, mean_pop.y, pot_ggg_pop.x, pot_ggg_pop.y))

afro_w8%<>%
  distinct(id_unique, .keep_all = TRUE)

@@

```{r}
data_trust_report_adm2 <- readRDS("Data/Data_RDS/data_trust_report_adm2.rds")

countries_adm2 <- c("BFA","GIN", "LBR", "NER", "SLE")
#No Botswana, Ivory Coast, Mali ,Togo in 2018

data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

data_trust%<>%
  select(-pot_ggg_pop, -pot_gg_pop, -pot_cvg, -mean_ggg, -mean_ggg_pop, -mean_gg, -mean_gg_pop, -mean_pop.x, mean)

data_trust%<>%
  select(-mean_ggg.x,
-mean_ggg_pop.x,
-pot_ggg_pop.x, 
-mean_pop.x,
-pot_ggg_pop.y, 
-mean_ggg_pop.y, 
-mean_pop.y, 
-mean_ggg.y)

data_trust%<>%
  select(
-mean_gg,
-mean_gg_pop,
-pot_gg_pop,
-pot_cvg)

@@

@@

@@

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

write_dta(data_trust, "Data/Data_dta/data_trust.dta")

@@

###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")

countries_adm1 <- c("GHA","KEN","MWI","NGA","TZA","UGA","ZMB", "ZWE")

data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
  mutate(round=7)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust %<>%
  mutate(mean_ggg = coalesce(mean_ggg.x, mean_ggg.y))%>%
  mutate(mean_ggg_pop = coalesce(mean_ggg_pop.x, mean_ggg_pop.y))%>%
  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
  mutate(pot_ggg_pop = coalesce(pot_ggg_pop.x, pot_ggg_pop.y))%>%
  select(-c(mean_ggg.x, mean_ggg.y, mean_ggg_pop.x,mean_ggg_pop.y, mean_pop.x, mean_pop.y, pot_ggg_pop.x, pot_ggg_pop.y))

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

write_dta(data_trust, "Data/Data_dta/data_trust.dta")

##2014
###ADM2
```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("GIN", "LBR", "NER")
#No Benin, Botswana, Cameroon, Ivory Coast, Mali, Namibia, Senegal, Togo in 2014

data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

@@

data_trust %<>%
  mutate(mean_ggg = coalesce(mean_ggg.x, mean_ggg.y))%>%
  mutate(mean_ggg_pop = coalesce(mean_ggg_pop.x, mean_ggg_pop.y))%>%
  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
  mutate(pot_ggg_pop = coalesce(pot_ggg_pop.x, pot_ggg_pop.y))%>%
  select(-c(mean_ggg.x, mean_ggg.y, mean_ggg_pop.x,mean_ggg_pop.y, mean_pop.x, mean_pop.y, pot_ggg_pop.x, pot_ggg_pop.y))

@@

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

write_dta(data_trust, "Data/Data_dta/data_trust.dta")

```
###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")

countries_adm1 <- c("KEN","NGA","UGA", "ZWE")
# No Mozambique in 2014

data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, pot_ggg_pop, mean_ggg_pop, mean_pop, mean_ggg)%>%
  mutate(round=6)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust %<>%
  mutate(mean_ggg = coalesce(mean_ggg.x, mean_ggg.y))%>%
  mutate(mean_ggg_pop = coalesce(mean_ggg_pop.x, mean_ggg_pop.y))%>%
  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
  mutate(pot_ggg_pop = coalesce(pot_ggg_pop.x, pot_ggg_pop.y))%>%
  select(-c(mean_ggg.x, mean_ggg.y, mean_ggg_pop.x,mean_ggg_pop.y, mean_pop.x, mean_pop.y, pot_ggg_pop.x, pot_ggg_pop.y))

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

write_dta(data_trust, "Data/Data_dta/data_trust.dta")

```
#2G Data

@@

```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
#No Senegal, Togo in 2019

@@

afro_w8 %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

glimpse(afro_w8)

afro_w8 %<>%
  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
  select(-c(mean_pop.x, mean_pop.y))

afro_w8%<>%
  distinct(id_unique, .keep_all = TRUE)
```

###ADM1
```{r}
countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
  mutate(round=8)

afro_w8 %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

glimpse(afro_w8)

afro_w8 %<>%
  mutate(mean_gg = coalesce(mean_gg.x, mean_gg.y))%>%
  mutate(mean_gg_pop = coalesce(mean_gg_pop.x, mean_gg_pop.y))%>%
  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
  mutate(pot_gg_pop = coalesce(pot_gg_pop.x, pot_gg_pop.y))%>%
  select(-c(mean_gg.x, mean_gg.y, mean_gg_pop.x,mean_gg_pop.y, mean_pop.x, mean_pop.y, pot_gg_pop.x, pot_gg_pop.y))

afro_w8%<>%
  distinct(id_unique, .keep_all = TRUE)
```

@@

```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BEN", "BFA", "BWA", "CMR", "CIV", "GIN", "LBR", "MLI","NAM", "NER", "SLE")
#No Senegal, Togo in 2016

data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

@@

@@

data_trust %<>%
  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
  select(-c(mean_pop.x, mean_pop.y))

@@

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

write_dta(data_trust, "Data/Data_dta/data_trust.dta")

###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")

countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

data_trust <- readRDS("Data/Data_RDS/data_trust.rds")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, pot_gg_pop, mean_gg_pop, mean_pop, mean_gg)%>%
  mutate(round=7)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust %<>%
  mutate(mean_gg = coalesce(mean_gg.x, mean_gg.y))%>%
  mutate(mean_gg_pop = coalesce(mean_gg_pop.x, mean_gg_pop.y))%>%
  mutate(mean_pop = coalesce(mean_pop.x, mean_pop.y))%>%
  mutate(pot_gg_pop = coalesce(pot_gg_pop.x, pot_gg_pop.y))%>%
  select(-c(mean_gg.x, mean_gg.y, mean_gg_pop.x,mean_gg_pop.y, mean_pop.x, mean_pop.y, pot_gg_pop.x, pot_gg_pop.y))

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

write_dta(data_trust, "Data/Data_dta/data_trust.dta")

@@

saveRDS(data_trust, file="Data/Data_RDS/data_trust.rds")

write_dta(data_trust, "Data/Data_dta/data_trust.dta")

###ADM1
```{r}
data_trust_report_adm1_valid <- readRDS("Data/Data_RDS/data_trust_report_adm1_valid.rds")
